This is the Title

### 2017-04-20 paper/paper-DrexelFormat.tex
updated paper rnn part

	To describe RNN in math equation, let $x^{t}$ be input data on time $t$, $h^{t}$ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$. The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output. The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The value for hidden layer can be calculated by $h^{t} = Ux^{t} + Wo^{t-1}$ then the output can be calculated by $o^{t} = Vh^{t}$. Therefore, RNN can be written in $o^{t} = V(Ux^{t} + Wo^{t-1})$

@@

>>>>

	To describe RNN in math equation, let $x^{t}$ be input data on time $t$, $h^{t}$ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$. The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output. The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The result from hidden layer can be calculated by 
	$$h^{t} = f(Ux^{t} + Wo^{t-1} + b_h)$$ where $f()$ is activation function for hidden layer and $b$ is bias for hidden layer. Then the output can be calculated by
	$$o^{t} = g(Vh^{t}+b_o)$$ where $g()$ is activation function for output layer and $b_o$ is bias for output layer. Therefore, RNN can be written in
	$$o^{t} = g(Vf(Ux^{t} + Wo^{t-1} + b_h) + b_o)$$

@@

	RNN is not always like the figure \ref{fig:unfold_RNN}. Input from previous output can be replaced by result of previous hidden layer. The main idea of RNN is when neural network decides current output it considers previous state.
